Redirecting Resolution Proofs

### 2011-09-02 bib/prooftransform/redirecting-proofs-2/paper.tex
minor fix to paper

In my PAAR 2010 and IWIL 2010 talks \cite{blanchette-paulson-2010,paulson-2010},
I sketched a method for transforming proofs by contradiction into direct proofs.
The method was very simple and simply exploited the contrapositive, but in the
worst case the resulting proof could explode exponentially in size. In this
paper, I propose a new method transform resolution proofs into direct proofs
expressed in a simple Isar-like syntax (Section~\ref{sec:proof-notations}),
based on a simple set of rules (Sections \ref{sec:introductory-examples} and
\ref{sec:the-algorithm}). The new approach is sound and complete and has the
advantage that each deduction in the ATP proof gives rise to exactly one
deduction in the direct proof. A linear number of additional steps are
introduced in the direct proof, but these are simple logical rules, such as
modus ponens, and do not require the full power of Metis.
%The approach is illustrated on
%actual ATP proofs found by Sledgehammer (Section~\ref{sec:gallery}).

@@

\begin{center}
\begin{tabular}{@{}p{.3\textwidth}@{}p{.3\textwidth}@{}}
\begin{tabular}{@{}l@{}}
\keyw{proof} -- \\
\hbox{}\quad \keyw{have}\, $4$ \keyw{\,by\,} \textit{metis} \\
\hbox{}\quad \keyw{hence}\, $3$ \keyw{\,by\,} (\textit{metis\, }$2$) \\
\hbox{}\quad \keyw{thus}\, $0$ \keyw{\,by\,} (\textit{metis\, }$1$) \\
\keyw{qed}
\end{tabular}
&
\begin{tabular}{@{}p{.25\textwidth}@{}p{.25\textwidth}@{}}
\frm \hav 4 \end
\frx 2 \hen 3 \end
\frx 1 \hen 0 \end
\end{tabular}
\end{tabular}
\end{center}

>>>>

In my PAAR 2010 and IWIL 2010 talks \cite{blanchette-paulson-2010,paulson-2010},
I sketched a method for transforming proofs by contradiction into direct proofs.
The method was very simple and simply exploited the contrapositive, but in the
worst case the resulting proof could explode exponentially in size. In this
paper, I propose a new method for transforming resolution proofs into direct
proofs expressed in a simple Isar-like syntax
(Section~\ref{sec:proof-notations}), based on a simple set of rules (Sections
\ref{sec:introductory-examples} and \ref{sec:the-algorithm}). The new approach
is sound and complete and has the advantage that each deduction in the ATP proof
gives rise to exactly one deduction in the direct proof. A linear number of
additional steps are introduced in the direct proof, but these are simple
logical rules, such as modus ponens, and do not require the full power of Metis.
%The approach is illustrated on
%actual ATP proofs found by Sledgehammer (Section~\ref{sec:gallery}).

@@

\begin{center}
\begin{tabular}{@{}p{.3\textwidth}@{}p{.3\textwidth}@{}}
\begin{tabular}{@{}l@{}}
\keyw{proof} -- \\
\hbox{}\quad \keyw{have}\, $4$ \keyw{\,by\,} (\textit{metis\, }$1$) \\
\hbox{}\quad \keyw{hence}\, $3$ \keyw{\,by\,} (\textit{metis\, }$2$) \\
\hbox{}\quad \keyw{thus}\, $0$ \keyw{\,by\,} (\textit{metis\, }$1$) \\
\keyw{qed}
\end{tabular}
&
\begin{tabular}{@{}p{.25\textwidth}@{}p{.25\textwidth}@{}}
\frm 1 \hav 4 \end
\frx 2 \hen 3 \end
\frx 1 \hen 0 \end
\end{tabular}
\end{tabular}
\end{center}
